### 2008-12-20 talk/ecoop2009/conclusion.tex
add high-level structure of conclusions

XXX add me

>>>>

high level structure:

1. We presented PyPy JIT generator

2. interpreters can exploit the JIT generator by placing few hints here and
there to guide the generation of code

3. generated JITs produce fast code thanks to \textbf{promotion} (our first
contribution) and automatic unboxing

4. we presented a way to implement promotion/flexswitches on top of .NET

5. our second contribution is to show that the idea of JIT layering can work
well, as for some cases we can get performances even better than C\#
